\bf Faster Neural Machine Translation Inference

### 2018-01-30 fast-beam/fast-beam.tex
begin matrix wrapper

Secondly, mini-batching is often used to increase the speed of deep-learning applications, including NMT systems. (??? graph of batch v. speed) shows using batching can increase speed by 17 times. However, mini-batching does not take into acccount the variable length of NMT inputs and outputs, creating computational issues and efficiency challenges. The computational issues are often solved by masking unwanted calculations. Translation speed can often be improved by employing max-batching whereby the input set is pre-sorted by sentence length before mini-batching, creating mini-batches with similar length input sentences. However, the target sentence lengths will still differ even for similar length inputs but the standard mini-batchin algorithm must continue to process the batch until all target sentences have been completed. (??? batchsize size v. iterations) shows the number of sentences still being processed for each decoding iteration, for a specific batch. The number of sentences still to be processed decreases, reducing the effectiveness of mini-batching. We will propose an alternative to the mini-batching algorithm.

We based our model on the sequence-to-sequence model of ~\cite{D14-1179} for machine translation models, but unlike ~\cite{DBLP:conf/emnlp/Devlin17}, we avoid solutions for the specific model. Therefore, our solution should be applicable to other models, architectures and task which have the similar characteristics. We envisage that our solutions would be of value to models used in text summarization, chatbot or image captioning. We also choose to focus on the use of GPU, rather than CPU as pursued in ~\cite{DBLP:conf/emnlp/Devlin17}.

>>>>

Secondly, the use of mini-batching is critical for fast model inference. However, mini-batching does not take into acccount variable sentence lengths which decrease the actual number of input or output sentences that are processed in parallel, negating the benefit of mini-batching. This can be partially reduced in the encoding with \emph{maxi-batching}, i.e. pre-sorting sentences by length before creating mini-batches with similar length source sentences. However, target sentence lengths will still differ even for similar length inputs, compromising decoding performance. Figure~\ref{fig:batch-size} shows the actual batch size during decoding with a maximum batch size of 128; in only 42\% of decoding iteration was batch full.

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{batch-size.png}} 
\end{tabular}
\caption{Actual batchsize during decoding (max batchsize 128, beam size 5, Europarl test set)}
\label{fig:batch-size}
\end{figure}

We will propose an alternative batching algorithm to increase the actual batch size during decoding.

We base our model on the sequence-to-sequence model of ~\cite{D14-1179} for machine translation models and also choose to focus on the using GPUs rather than CPUs as pursued by ~\cite{DBLP:conf/emnlp/Devlin17}.
